EasyMerge - A New Tool for Code Clones Refactoring

### 2014-03-17 paper/paper.tex
updates

There are five text boxes displayed on the main interface.
Once the scanning phase is completed, a list of refactorable clone sets are displayed in the ``Possible Merges" box at top left.
All items in the list are initially coloured green, once a merge is done, the colour will be changed to red for the record.

@@

Last but not least, the ``Extracted Method" box display the extracted method we generated as a helper function all code replacement 
in original source code files are calling. After reviewing all information and recommendation we provide, a user can perform the code refactoring for
a certain set by clicking ``Merge" button on bottom left. 
EasyMerge in turn will rewrite the source files and move the generated helper to our specific accessible file in back-end.
And all merging done in current session can be redone by clicking ``Unmerge" button if
the user performed an unwanted merge.

>>>>

There are five window boxes displayed on the main interface.
Once the scanning phase is completed, a list of refactorable clone sets are displayed in the ``Possible Merges" box at top left.
All items in the list are initially coloured green, once a merge is done, the colour will be changed to red for the record.

@@

Last but not least, the ``Extracted Method" box display the extracted method we generated as a helper function all code replacement 
in original source code files are calling. After reviewing all information and recommendation we provide, a user can perform the code refactoring for
a certain set by clicking ``Merge" button on bottom left. 
EasyMerge in turn will rewrite the source files and move the generated helper to our specific accessible file in back-end.
And all merging done in current session can be redone by clicking ``Unmerge" button if
the user performed an unwanted merge for a certain set.
